\bf A Comparision of Bootstrap Confidence Interval Methods

### 2022-12-09 project/PaperTemplate/paper.tex
Minor edits

\bigskip
\begin{abstract}
This paper explores different bootstrap methods for creating confidence
intervals and tests their performance against each other for different
types of distributions. This paper will re-introduce the ideas of
bootstraps and confidence intervals, as well as the theory behind
different methods of bootstrapped confidence intervals. Along with the
theoretical details of each method, we will provide an example of each
bootstrapped confidence interval method with a toy dataset. Then, we
will run a simulation that evaluates the performance of a couple of the
methods we introduced on a variety of sample sizes and types of
distributions.
\end{abstract}

@@

We demonstrate performing a non-parametric bootstrap below using
\texttt{SnowGR}, which gives the official snowfall dataset by the month
for Grand Rapids, MI, starting in 1893. We will be using the
\texttt{Dec} variable, which is the number of inches of snow that fell
in December of each year. In particular, we are interested in the sample
mean and later finding confidence intervals for the population mean of
\texttt{Dec}. The distribution is shown (Figure 1).

@@

\includegraphics{paper_files/figure-latex/SnowGR histogram-1.pdf} Next,
we will perform the non-parametric bootstrap using 10,000 replications.

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{set.seed}\NormalTok{(}\DecValTok{495}\NormalTok{)}
\NormalTok{orig\_mean }\OtherTok{\textless{}{-}} \FunctionTok{mean}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\CommentTok{\# theta hat}

\FunctionTok{set.seed}\NormalTok{(}\DecValTok{495}\NormalTok{)}
\NormalTok{nboot }\OtherTok{\textless{}{-}} \DecValTok{10000}

\NormalTok{mean }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,nboot)}
\NormalTok{sd }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,nboot)}
\NormalTok{se }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,nboot)}
\NormalTok{t\_stat }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,nboot)}

\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{nboot) \{}
\NormalTok{  resampled }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(mosaic}\SpecialCharTok{::}\FunctionTok{resample}\NormalTok{(SnowGR, }\AttributeTok{replace =} \ConstantTok{TRUE}\NormalTok{))}
\NormalTok{  mean[i] }\OtherTok{\textless{}{-}} \FunctionTok{mean}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{Dec, }\AttributeTok{data =}\NormalTok{ resampled)}
\NormalTok{  sd[i] }\OtherTok{\textless{}{-}} \FunctionTok{sd}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{Dec, }\AttributeTok{data =}\NormalTok{ resampled)}
\NormalTok{\}}

\NormalTok{dec\_means }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(mean)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{gf\_histogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in December"}\NormalTok{, }
       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in December"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{,}
       \AttributeTok{caption =} \StringTok{"Fig. 3: Histogram with Standard Interval Shown"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{13.85639}\NormalTok{)) }\SpecialCharTok{+}
  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{17.65957}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{gf\_histogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in December"}\NormalTok{, }
       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in December"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{,}
       \AttributeTok{caption =} \StringTok{"Fig. 4: Histogram with Percentile Interval Shown"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{13.91170}\NormalTok{)) }\SpecialCharTok{+}
  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{17.72353}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{paper_files/figure-latex/unnamed-chunk-5-1.pdf} This
interval is similar to the one created using the standard method, but
shifted slightly to the right.

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{gf\_histogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in December"}\NormalTok{, }
       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in December"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{,}
       \AttributeTok{caption =} \StringTok{"Fig. 5: Histogram with BC Interval Shown"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{14.01172}\NormalTok{)) }\SpecialCharTok{+}
  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{17.82017}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{gf\_histogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in December"}\NormalTok{, }
       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in December"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{,}
       \AttributeTok{caption =} \StringTok{"Fig. 6: Histogram with BCa Interval Shown"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{13.91591}\NormalTok{)) }\SpecialCharTok{+}
  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{17.72353}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{gf\_histogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in December"}\NormalTok{, }
       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in December"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{, }
       \AttributeTok{caption =} \StringTok{"Fig. 7: Histogram with Studentized Interval Shown"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{14.03467}\NormalTok{)) }\SpecialCharTok{+}
  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{18.01709}\NormalTok{)) }
\end{Highlighting}
\end{Shaded}

@@

For our simulation, we will randomly sample from distributions in which
we know the true population mean. For example, we will be sampling from
a Gamma distribution where we can find the true population mean using
the shape and rate parameters of the sample distribution. After we
sample from the distribution, we will create a bootstrapped confidence
interval for a few of the methods we described in the exposition. Since
we know the true population mean of the distribution, we will determine
if the true population mean is contained in the confidence interval for
each of the methods we are testing \citep{Guillaume21}. We will perform
this process a large number of times (10,000 simulations) and then
average by the number of iterations to determine, on average, the
proportion that each bootstrapped confidence interval method contains
the true population mean for a given distribution. We will do this for a
couple of different distributions and ranges of sample sizes to show how
the intervals perform with skewed distributions and larger sample sizes.

To do this simulation, we will use the \texttt{boot} package
\citep{boot}. This package can compute a bootstrap object which contains
the output from a bootstrap calculation of a given sample and then
produces confidence intervals from the bootstrap object. In particular,
we will use the \texttt{boot.ci} function to create four confidence
intervals: the standard (or normal) confidence interval, the studentized
confidence interval, the percentile confidence interval, and the
bias-corrected with acceleration confidence interval.

@@

  \CommentTok{\# initialize matrix to hold different bootstrap prop. for each sample size}

@@

    \CommentTok{\# initialize vectors that hold if the CI contains true mean by iteration}

@@

\NormalTok{normal\_fig }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(}\AttributeTok{data =}\NormalTok{ normal\_df\_long, }
                    \FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ Sample\_Size, }\AttributeTok{y =}\NormalTok{ prop, }\AttributeTok{color =}\NormalTok{ method)) }\SpecialCharTok{+} 
  \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+} \FunctionTok{geom\_line}\NormalTok{() }\SpecialCharTok{+} 
  \FunctionTok{labs}\NormalTok{(}
    \AttributeTok{title =} \StringTok{"Prop. of CIs that Contain the True Mean from Normal Distibution"}\NormalTok{, }
    \AttributeTok{x =} \StringTok{"Sample Size"}\NormalTok{, }
    \AttributeTok{y =} \StringTok{"Proportion (of 10,000 Simulations)"}\NormalTok{, }\AttributeTok{color =} \StringTok{"Method"}\NormalTok{,}
    \AttributeTok{caption =} \StringTok{"Fig. 8: Graph showing the Accuracy of Bootstrap CI Methods for}
\StringTok{       different sample sizes on Normal Dist."}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{theme\_light}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position=}\StringTok{"bottom"}\NormalTok{)}

@@

\NormalTok{gamma\_fig }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(}\AttributeTok{data =}\NormalTok{ gamma\_df\_long, }
                    \FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ Sample\_Size, }\AttributeTok{y =}\NormalTok{ prop, }\AttributeTok{color =}\NormalTok{ method)) }\SpecialCharTok{+} 
  \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+} \FunctionTok{geom\_line}\NormalTok{() }\SpecialCharTok{+} 
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Prop. of CIs that Contain the True Mean from Gamma Distibution"}\NormalTok{, }
       \AttributeTok{x =} \StringTok{"Sample Size"}\NormalTok{, }
       \AttributeTok{y =} \StringTok{"Proportion (of 10,000 Simulations)"}\NormalTok{, }\AttributeTok{color =} \StringTok{"Method"}\NormalTok{,}
       \AttributeTok{caption =} \StringTok{"Fig. 9: Graph showing the Accuracy of Bootstrap CI Methods for }
\StringTok{       different sample sizes on Gamma Dist."}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{theme\_light}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position=}\StringTok{"bottom"}\NormalTok{)}

@@

\NormalTok{log\_normal\_fig }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(}\AttributeTok{data =}\NormalTok{ log\_normal\_df\_long, }
                    \FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ Sample\_Size, }\AttributeTok{y =}\NormalTok{ prop, }\AttributeTok{color =}\NormalTok{ method)) }\SpecialCharTok{+} 
  \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+} \FunctionTok{geom\_line}\NormalTok{() }\SpecialCharTok{+} 
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =}\StringTok{"Prop. of CIs that Contain True Mean from Log{-}Normal Distibution"}\NormalTok{,}
       \AttributeTok{x =} \StringTok{"Sample Size"}\NormalTok{, }
       \AttributeTok{y =} \StringTok{"Proportion (of 10,000 Simulations)"}\NormalTok{, }\AttributeTok{color =} \StringTok{"Method"}\NormalTok{,}
       \AttributeTok{caption =} \StringTok{"Fig. 10: Graph showing the Accuracy of Bootstrap CI Methods }
\StringTok{       for different sample sizes on Log{-}Normal Dist."}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{theme\_light}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position=}\StringTok{"bottom"}\NormalTok{)}

>>>>

\bigskip
\begin{abstract}
This paper explores different bootstrap methods for creating confidence
intervals and tests their performance against each other for different
types of distributions. This paper will re-introduce the idea of
bootstraps and confidence intervals, as well as the theory behind
different methods of bootstrapped confidence intervals. Along with the
theoretical details of each method, we will provide an example of each
bootstrapped confidence interval method using a toy dataset. Then, we
will run a simulation that evaluates the performance of a couple of the
methods on a variety of sample sizes and types of distributions.
\end{abstract}

@@

We demonstrate performing a non-parametric bootstrap below using
\texttt{SnowGR}, which gives the official snowfall dataset by the month
for Grand Rapids, MI, starting in 1893 and is found in the
\texttt{mosaic} package \citep{mosaic}. We will be using the
\texttt{Dec} variable, which is the number of inches of snow that fell
in December of each year. In particular, we are interested in the sample
mean and later finding confidence intervals for the population mean of
\texttt{Dec}. The distribution is shown (Figure 1).

@@

\includegraphics{paper_files/figure-latex/SnowGR histogram-1.pdf}

Next, we will perform the non-parametric bootstrap using 10,000
replications.

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{set.seed}\NormalTok{(}\DecValTok{495}\NormalTok{)}
\NormalTok{orig\_mean }\OtherTok{\textless{}{-}} \FunctionTok{mean}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\CommentTok{\# theta hat}
\NormalTok{nboot }\OtherTok{\textless{}{-}} \DecValTok{10000}
\CommentTok{\# initialize storage vectors}
\NormalTok{mean }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,nboot)}
\NormalTok{sd }\OtherTok{\textless{}{-}} \FunctionTok{rep}\NormalTok{(}\DecValTok{0}\NormalTok{,nboot)}

\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{nboot) \{}
\NormalTok{  resampled }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(mosaic}\SpecialCharTok{::}\FunctionTok{resample}\NormalTok{(SnowGR, }\AttributeTok{replace =} \ConstantTok{TRUE}\NormalTok{))}
\NormalTok{  mean[i] }\OtherTok{\textless{}{-}} \FunctionTok{mean}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{Dec, }\AttributeTok{data =}\NormalTok{ resampled)}
\NormalTok{  sd[i] }\OtherTok{\textless{}{-}} \FunctionTok{sd}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{Dec, }\AttributeTok{data =}\NormalTok{ resampled)}
\NormalTok{\}}
\NormalTok{dec\_means }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(mean)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{gf\_histogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in December"}\NormalTok{, }
       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in December }
\StringTok{       with Standard Interval"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{,}
       \AttributeTok{caption =} \StringTok{"Fig. 3: Histogram with Standard Interval Shown"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{13.85639}\NormalTok{)) }\SpecialCharTok{+}
  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{17.65957}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{gf\_histogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in December"}\NormalTok{, }
       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in December}
\StringTok{       with Percentile Interval"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{,}
       \AttributeTok{caption =} \StringTok{"Fig. 4: Histogram with Percentile Interval Shown"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{13.91170}\NormalTok{)) }\SpecialCharTok{+}
  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{17.72353}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\includegraphics{paper_files/figure-latex/unnamed-chunk-5-1.pdf}

This interval is similar to the one created using the standard method,
but shifted slightly to the right.

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{gf\_histogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in December"}\NormalTok{, }
       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in December}
\StringTok{       with BC interval"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{,}
       \AttributeTok{caption =} \StringTok{"Fig. 5: Histogram with BC Interval Shown"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{14.01172}\NormalTok{)) }\SpecialCharTok{+}
  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{17.82017}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{gf\_histogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in December"}\NormalTok{, }
       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in December}
\StringTok{       with BCa interval"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{,}
       \AttributeTok{caption =} \StringTok{"Fig. 6: Histogram with BCa Interval Shown"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{13.91591}\NormalTok{)) }\SpecialCharTok{+}
  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{17.72353}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{gf\_histogram}\NormalTok{(}\SpecialCharTok{\textasciitilde{}}\NormalTok{ Dec, }\AttributeTok{data =}\NormalTok{ SnowGR) }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{x =} \StringTok{"Annual Snowfall in December"}\NormalTok{, }
       \AttributeTok{title =} \StringTok{"Distribution of Annual Snowfall in December}
\StringTok{       with Studentized Interval"}\NormalTok{, }\AttributeTok{y =} \StringTok{"Count"}\NormalTok{, }
       \AttributeTok{caption =} \StringTok{"Fig. 7: Histogram with Studentized Interval Shown"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{14.03467}\NormalTok{)) }\SpecialCharTok{+}
  \FunctionTok{geom\_vline}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{xintercept=} \FloatTok{18.01709}\NormalTok{)) }
\end{Highlighting}
\end{Shaded}

@@

For our simulation, we will randomly sample from distributions in which
we know the true population mean. For example, we will be sampling from
a Gamma distribution where we can find the true population mean using
the shape and rate parameters of the sample distribution. After we
sample from the distribution, we will create a bootstrapped confidence
interval for a few of the methods we described in the exposition. Since
we know the true population mean of the distribution, we will determine
if the true population mean is contained in the confidence interval for
each of the methods we are testing \citep{Guillaume21}. We will perform
this process a large number of times (10,000 simulations) and then
average by the number of iterations to determine, on average, the
proportion that each bootstrapped confidence interval method contains
the true population mean for a given distribution. We will do this for a
couple of different distributions and ranges of sample sizes to show how
the intervals perform with skewed distributions and larger sample sizes.
We will define the accuracy of each method as the proportion that each
bootstrapped confidence interval method contains the true population
mean for a distribution

To perform this simulation, we will use the \texttt{boot} package
\citep{boot}. This package can compute a bootstrap object which contains
the output from a bootstrap calculation of a given sample and then
produces confidence intervals from the bootstrap object. In particular,
we will use the \texttt{boot.ci} function to create four confidence
intervals: the standard (or normal) confidence interval, the studentized
confidence interval, the percentile confidence interval, and the
bias-corrected with acceleration confidence interval.

@@

  \CommentTok{\# initialize matrix to hold different bootstrap prop. }
  \CommentTok{\# for each sample size}

@@

    \CommentTok{\# initialize vectors that hold if the CI contains true mean }
    \CommentTok{\# by iteration}

@@

\NormalTok{normal\_fig }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(}\AttributeTok{data =}\NormalTok{ normal\_df\_long, }
                    \FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ Sample\_Size, }\AttributeTok{y =}\NormalTok{ prop, }\AttributeTok{color =}\NormalTok{ method)) }\SpecialCharTok{+} 
  \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+} \FunctionTok{geom\_line}\NormalTok{() }\SpecialCharTok{+} 
  \FunctionTok{labs}\NormalTok{(}
    \AttributeTok{title =} \StringTok{"Accuracy of Bootstrap CIs using Normal Distibution"}\NormalTok{, }
    \AttributeTok{x =} \StringTok{"Sample Size"}\NormalTok{, }
    \AttributeTok{y =} \StringTok{"Proportion (of 10,000 Simulations)"}\NormalTok{, }\AttributeTok{color =} \StringTok{"Method"}\NormalTok{,}
    \AttributeTok{caption =} \StringTok{"Fig. 8: Graph showing the Accuracy of Bootstrap CI }
\StringTok{    Methods for different sample sizes on Normal Distribution"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{theme\_light}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position=}\StringTok{"bottom"}\NormalTok{)}

@@

\NormalTok{gamma\_fig }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(}\AttributeTok{data =}\NormalTok{ gamma\_df\_long, }
                    \FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ Sample\_Size, }\AttributeTok{y =}\NormalTok{ prop, }\AttributeTok{color =}\NormalTok{ method)) }\SpecialCharTok{+} 
  \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+} \FunctionTok{geom\_line}\NormalTok{() }\SpecialCharTok{+} 
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Accuracy of Bootstrap CIs using Gamma Distibution"}\NormalTok{, }
       \AttributeTok{x =} \StringTok{"Sample Size"}\NormalTok{, }
       \AttributeTok{y =} \StringTok{"Proportion (of 10,000 Simulations)"}\NormalTok{, }\AttributeTok{color =} \StringTok{"Method"}\NormalTok{,}
       \AttributeTok{caption =} \StringTok{"Fig. 9: Graph showing the Accuracy of Bootstrap CI }
\StringTok{       Methods for different sample sizes on Gamma Distribution"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{theme\_light}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position=}\StringTok{"bottom"}\NormalTok{)}

@@

\NormalTok{log\_normal\_fig }\OtherTok{\textless{}{-}} \FunctionTok{ggplot}\NormalTok{(}\AttributeTok{data =}\NormalTok{ log\_normal\_df\_long, }
                    \FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ Sample\_Size, }\AttributeTok{y =}\NormalTok{ prop, }\AttributeTok{color =}\NormalTok{ method)) }\SpecialCharTok{+} 
  \FunctionTok{geom\_point}\NormalTok{() }\SpecialCharTok{+} \FunctionTok{geom\_line}\NormalTok{() }\SpecialCharTok{+} 
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =}\StringTok{"Accuracy of Bootstrap CIs using Log{-}Normal }
\StringTok{       Distibution"}\NormalTok{,}
       \AttributeTok{x =} \StringTok{"Sample Size"}\NormalTok{, }
       \AttributeTok{y =} \StringTok{"Proportion (of 10,000 Simulations)"}\NormalTok{, }\AttributeTok{color =} \StringTok{"Method"}\NormalTok{,}
       \AttributeTok{caption =} \StringTok{"Fig. 10: Graph showing the Accuracy of Bootstrap CI }
\StringTok{       Methods for different sample sizes on Log{-}Normal Distribution"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{theme\_light}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{theme}\NormalTok{(}\AttributeTok{legend.position=}\StringTok{"bottom"}\NormalTok{)}
